What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Spellcheck and minor tweaks

\resolved{too much emphasis on {\em how}... rewrite following paragrapgh}

@@

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approxmately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particulary topical at particular times (Section~\ref{analysis}).

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarisation of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.

\resolved{All merged? : The methods we use are closely related to related work on information extraction which is the task of identifing and classifing specific semantic entities within documents (i.e. names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}

@@

It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behaviour by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first). Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retreived by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).

@@

The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambigous.

@@

We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

@@

Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambigous. This is not surprising. We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambigous.

@@

\section{Analysing the Data}
\label{analysis}
\input{analysis.tex}

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambigous disputable claims. Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.

@@

MemeTracker~\cite{Backstrom2009} produced vaguely similar graphs, showing when particular memes were widely discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims.

@@

For each noun, we analysed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed. Rather than clustering claims directly, we instead cluster together words that frequently co-occur. We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. Most of these will make sense to people who have been following news in the united states. For example, we see that disputed claims about Obama often talk about his nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.

>>>>

\resolved{too much emphasis on {\em how}... rewrite following paragraph}

@@

We believe that this corpus will be useful for many purposes. We are currently using it as part of our Dispute Finder~\cite{Ennals2010} project to automatically highlight phrases on web pages that are disputed by other sources. We are also exploring other applications of this corpus, including automatically detecting disputed claims in human speech, visualization tools that let users know what is disputed about a topic that interests them, and statistical tools that allow people to look for patterns in Internet debate  (Section~\ref{using}).

We have made our corpus publicly available for other researchers to download at \url{http://confront.intel-research.net/}. It currently contains claims extracted from pages written on the days between October 1st 2009 and January 19th 2010, and pages written on January 10th of every year from 2000 to 2010. This amounts to approximately 1.1 million strings that we believe are making disputed claims. We plan to expand our corpus as we crawl more of the web and improve our algorithms.

By looking at the claims in this corpus, we see trends in dispute on the web that correspond to the debates that were particularly topical at particular times (Section~\ref{analysis}).

@@

The problem of determining information credibility on the web is becoming increasingly important. In the past a user would typically obtain information from a relatively small set of sources such as books, TV channels, and radio stations. The user would have some idea of the reputation and biases of each of these sources, and publishing barriers and quality control would ensure that these sources only published information that met their standards. 
The web is very different. A user has access to a vast number of different sources, but knows little about the biases or reputation of most of them. Moreover, the Internet has little in the way of publishing barriers or quality control. If a user is to extract reliable information from the web, they need to either restrict themselves to a small set of trusted sources, or use some kind of mechanism to determine the credibility of the information that they access.

@@

Another closely related area is sentiment analysis/opinion mining~\cite{Hu2004,Pang2004}. Opinion mining tries to determine what an author's opinion is about certain objects or certain features of certain objects. A focal application has been the automatic summarization of product reviews, to produce an overview of the product features that are viewed favorably or negatively. Dispute mining could be thought of as opinion mining applied to beliefs and ideas, rather than features of objects.

\resolved{All merged? : The methods we use are closely related to related work on information extraction which is the task of identifying and classifying specific semantic entities within documents (i.e. names of locations, people, organizations, temporal expressions etc.) We described such related work in the next Section.}

@@

It is useful to be able to update our corpus as new pages appear on the web, without having to repeatedly download the same pages. The Yahoo BOSS API does not offer the ability to request only recent pages, or to specify a particular date range. We instead simulate this behavior by including a literal date string in the queries we pass to Yahoo BOSS. For example, if we want to find claims that were disputed on January 10th 2010, then rather than searching for \texttt{``it is not true that''}, we instead search for \texttt{``it is not true that'' ``January 4 2010''}.

The reasoning behind this technique is that many articles on the web include the date the article was posted in the text of the web page, particularly news articles and blog posts. This approach has false positives and false negatives. Some web pages include dates that are not the date the article was posted, some web pages do not include the date the article was posted, and many web pages include dates in a different format. We recognize that our current implementation suffers from a systematic bias towards sites that write their dates in US format (month first) rather than UK format (day first). Despite being very primitive, this method seems to work reasonably well. When we manually inspected 50 pages retrieved by our algorithm, we found that 92\% written on the correct year, and 74\% were written in the correct month (Figure~\ref{dateaccuracy}).

@@

The {\it P} column in Figure~\ref{templates} shows the percentage of the strings that match each pattern that we estimate to be unambiguous falsifiable claims. We estimated the precision of each pattern by randomly selecting 100 strings that match the pattern and then manually marking strings that we subjectively decided were well formed and unambiguous.

@@

We built a statistical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. This is a classical text classification task; here the text is classified as either being an unambiguous falsifiable claim or an invalid one (binary classification). Naive Bayes classifiers\cite{duda} have been used extensively for language tasks (for example, to decide whether an email is spam or not~\cite{Sahami98abayesian} and to decide the topic of documents\cite{mccallum98comparison}). We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

@@

Manual inspection suggests that the classifier is fairly good at filtering out strings that are not claims (case 1) but does poorly at working out whether a claim is unambiguous. This is not surprising. We anticipate that a more sophisticated technique with real world knowledge would be needed in order to determine whether a claim was unambiguous.

@@

\section{Analyzing the Data}
\label{analysis}
\input{analysis.tex}

We downloaded all text strings that matched each of our 54 patterns for all dates from October 1st 2009 to January 19th 2010, and for January 10th of every year from 2000 to 2010. This gave us a total of 1.8 million text strings, of which 1.1 million were identified by our classifier as being unambiguous disputable claims. Of those 1.1 million text strings, most are repeating claims made elsewhere in the data set.

@@

These graphs resemble those produced by MemeTracker~\cite{Backstrom2009}, which graphed when particular memes were discussed on the web. They tracked highly repeated phrases, rather than nouns used in disputed claims.

@@

For each noun, we analyzed the claims about that noun, and produced clusters that represent claims about that noun that seem to be particularly hotly disputed. Rather than clustering claims directly, we instead cluster together words that frequently co-occur. We used an agglomerative clustering algorithm, repeatedly merging the two clusters of words that had the most claims in common.

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. Most of these will make sense to people who have been following news in the united states. For example, we see that disputed claims about Obama often talk about his Nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.
